Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-17 nips_2018.tex
updates to list section

\subsection{List Processing}\label{listSection}
Synthesizing programs that manipulate data structures is a widely studied
problem in the programming languages community~\cite{feser2015synthesizing}.
%with applications to computer aided programming~\cite{solar2008program}.
We consider this problem within the context of learning functions that
manipulate lists.
We created 236 Lisp-style list manipulation tasks, each with 15 input/output
examples (Tbl.~\ref{listexamples}).
Our data set is challenging along two dimensions: many of the functions are
very complicated, and the agent must learn to solve these complicated
problems from only 236 tasks.
Our data set primarily consists of arithmetic operations upon sequences, and
so, in addition to the Lisp primitives provided for the text editing
experiments, we additionally start the system out with the following
primitives:
\code{mod}, \code{*}, \code{>}, \code{is-square}, \code{is-prime}, \code{2},
\code{3}, \code{4}, \code{5}.

A complete repertoire of higher-order functions is a staple of functional
programming standard libraries.
Although we provided \system with some of the standard higher-order
functions, like \code{foldr} and \code{unfold}, we did not include others.
When trained on these list functions, our system rediscovers and then reuses
the higher-order function \code{filter} \textbf{Lucas: not sure if it
actually does this! It would be cool if we can write something like this
though.}

%% Our list function domain consists of hand-designed concepts from which we
%% sample tasks, so there is no ``ground truth'' formal DSL from which these
%% tasks are generated. Additionally, few of these tasks are concatenative ---
%% many of them represent distinct operations.
%% Tasks in this domain are solved by functions that take as input an integer
%% or a list of integers, and have as output either a Boolean, an integer, a
%% list of Booleans, or a list of integers.  There are 225 tasks in total, some
%% of which are shown in Tbl.~\ref{listexamples}.

%% We evaluate \system starting from two different initial DSLs, \emph{base} and
%% \emph{rich}. The base DSL starts with only
%% low-level primitives such as \code{mapi}, \code{reducei}, and
%% \code{if}, whereas the rich DSL includes some common structure that can be
%% built from these such as \code{all}, \code{filter}, \code{slice}, and
%% \code{index}.
%% Both are capable of solving all tasks supplied by our dataset.
%% See Supplement for details on these DSLs.

%% We found  this domain  difficult to tackle without starting from 
%% the rich DSL. Our
%% algorithm, like human learners, requires a spectrum of problems ranging from
%% easy to hard.
%% When starting with the base DSL,
%% we found that there were not enough steppingstones in the curriculum to
%% get \system off the ground.

%The behavior with the base DSL illustrates this phenomena  because the initial set of
%primitives is not paired with a sufficiently large and graded curriculum.

\begin{figure*}
\makebox[\textwidth][c]{
\begin{minipage}{0.6\textwidth}
  \begin{tabular}{lll}
    \toprule
    Name & Input & Output \\\midrule
    has-2 & [4\, 5\, 7\, 4] & \code{false} \\
    repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
    drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
    count-head-in-tail & [1\, 2\, 1\, 1\, 3] & 2 \\
    rotate-2 & [8\, 14\, 1\, 9] & [1\, 9\, 8\, 14] \\
    keep-mod-5 & [5\, 9\, 14\, 6\, 3\, 0] & [5\, 0] \\
    \bottomrule
  \end{tabular}
  \captionof{table}{Sample tasks from our list function domain}
  \label{listexamples}
\end{minipage}
\hfill
\begin{minipage}{0.6\textwidth}
  \centering
  \begin{tabular}{l}
    \toprule
    $f_0($\code{i$,\ell$}$) \,=\, $\code{(TODO)}\\
    \hspace{0.5cm}($f_0$: \emph{TODO})\\
  \bottomrule
  \end{tabular}
  \captionof{table}{Some learned DSL primitives for list functions}\label{listinduced}
\end{minipage}
  }
\end{figure*}

\subsection{Text Editing}\label{textSection}
Synthesizing programs that edit text is a classic problem in the
programming languages and AI literatures~\cite{menon2013machine,lau2001programming},
and algorithms that learn text editing programs ship in Microsoft Excel~\cite{gulwani2011automating}.
This prior work presumes a hand-engineered DSL.
We show \system can instead start out with generic Lisp primitives
and recover many of the higher-level building blocks that have made these
other systems successful.

>>>>

\subsection{List Processing}\label{listSection}
Synthesizing programs that manipulate data structures is a widely studied
problem in the programming languages community~\cite{feser2015synthesizing}.
%with applications to computer aided programming~\cite{solar2008program}.
We consider this problem within the context of learning functions that
manipulate lists with some involvement of numerical arithmetic.

\begin{wrapfigure}{r}{0.55\textwidth}\centering
  \begin{tabular}{lll}
    \toprule
    Name & Input & Output \\\midrule
    repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
    drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
    rotate-2 & [8\, 14\, 1\, 9] & [1\, 9\, 8\, 14] \\
    count-head-in-tail & [1\, 2\, 1\, 1\, 3] & 2 \\
    keep-mod-5 & [5\, 9\, 14\, 6\, 3\, 0] & [5\, 0] \\
    product & [7\, 1\, 6\, 2] & 84 \\
    \bottomrule
  \end{tabular}
  \captionof{table}{Some tasks in our list function domain}
  \label{listexamples}
\end{wrapfigure}
We created 236 human-interpretable list manipulation tasks, each with 15
input/output examples (Tbl.~\ref{listexamples}).
Our data set is challenging in three major ways: many of the tasks require
complex solutions, the tasks were not generated from some latent DSL, and
the agent must learn to solve these complicated problems from only 236
tasks.
Our data set assumes arithmetic operations as well as sequence operations,
so we additionally provide our system with the following arithmetic
primitives: \code{mod}, \code{*}, \code{>}, \code{is-square},
\code{is-prime}.

\subsection{Text Editing}\label{textSection}
Synthesizing programs that edit text is a classic problem in the
programming languages and AI literatures~\cite{menon2013machine,lau2001programming},
and algorithms that learn text editing programs ship in Microsoft Excel~\cite{gulwani2011automating}.
This prior work presumes a hand-engineered DSL.
We show \system can instead start out with generic sequence manipulation
primitives and recover many of the higher-level building blocks that have
made these other text editing systems successful.
